WordRec Experiment

### 2019-05-14 Analysis/process.Rmd
cogsci camera ready

#The following is a test with adult pilot data
d_adult <- read_delim("adults_final.txt", delim = " ")  %>%
#d_adult <- read_delim("adult_pilot_3.txt", delim = " ")  %>%
  filter(type == "Test", #Here I will  filter out particiapants whose first language is arabic or hindi
         other != "yes") %>%
  mutate(iscorrect=ifelse(answer==correct, 1, 0))

@@

d_adult_good <- d_adult %>%
  left_join(d_adult_excl) %>%
  filter(score ==1) %>%
  filter(sound_dist != 'catch')

#feather::write_feather(d_adult_good, "../saved_data/data_adult.feather")
```

@@

#feather::write_feather(d_child_good, "../saved_data/data_child.feather")

@@

Plot children
```{r fig.width=5, fig.height=4}

@@

plot_child <- ggplot(sum_child, 
      aes(x = sound_dist, y = mean, group = factor(concept_dist), col = factor(concept_dist))) +
  #geom_point()+
  geom_pointrange(aes(ymin = lower, ymax = upper), 
                 position = position_dodge(width = .1)) + 
  geom_line() + 
  geom_hline(yintercept = 0.50, linetype="dashed") +
  xlab("Auditory similary") +ylab("Accuracy")+
  scale_colour_discrete(name="Visual similarity")+
  theme_few()+
theme(legend.title = element_text(size=11),
      legend.text=element_text(size=11),
      axis.text = element_text(size = 11)
      ) #+ facet_grid(.~block)

@@

  #scale_y_continuous(limits = c(0.45, 0.9))+
  theme_few()+
theme(legend.title = element_text(size=11),
      legend.text=element_text(size=11),
      axis.text = element_text(size = 11)
      ) #+ facet_grid(. ~ concept)

@@

Models
```{r}

@@

#Combine both  
data_both_ch <- data_ch %>%
  select(ID, c_dist, s_dist, item_object, item_sound, iscorrect) %>%
  mutate(age = -1)

@@

```{r}
#Process the data to prepare for the fit
data_fit_adult <- sum_adult %>%
  rename(lower  = lower.ci,
         upper = upper.ci) %>%
  mutate(group = 'adults',
         s_dist = ifelse(sound_dist =='different',  0.66, 0.23),
         c_dist = ifelse(concept_dist =='different', 0.40, 0.19))

data_fit_child <- sum_child %>% 
   mutate(group = 'children',
         s_dist = ifelse(sound_dist =='different',  1, 0.66),
         c_dist = ifelse(concept_dist =='different', 1, 0.40))

@@

Now I need to predict accuracy as a function of sound and meaning similarity 
```{r}

@@

@@

@@

Vr_ad <- coef(fit_adults)
Vr_s_ad <- coef(fit_adults_2)[1]
Vr_o_ad <- coef(fit_adults_2)[2]

@@

@@

Vr_ch <- coef(fit_children)
Vr_s_ch <- coef(fit_children_2)[1]
Vr_o_ch <- coef(fit_children_2)[2]

@@

@@

model_comparison <- tibble::rownames_to_column(AIC(fit_adults, fit_adults_2), 'model') %>%
  bind_rows(tibble::rownames_to_column(AIC(fit_children, fit_children_2), 'model'))

feather::write_feather(model1_val, "../saved_data/values_mod1.feather")       
feather::write_feather(model2_val, "../saved_data/values_mod2.feather")

feather::write_feather(model_comparison, "../saved_data/model_comparison.feather")

@@

model_data <- data_fit %>%
  mutate(prediction = ifelse(group=='adults', 
                             combine_cues(s_dist, c_dist, Vr_ad),
                             combine_cues(s_dist, c_dist, Vr_ch)
                             )) %>%
  mutate(prediction_2 = ifelse(group=='adults', 
                             combine_cues_2(s_dist, c_dist, Vr_s_ad, Vr_o_ad),
                             combine_cues_2(s_dist, c_dist, Vr_s_ch, Vr_o_ch)
                             )) %>%
  rename(human = mean)

feather::write_feather(model_data, "../saved_data/data_correlations.feather")

model_data_plot <-  model_data %>%
  gather(key, value, human, prediction, prediction_2) %>%
  mutate(ci.upper = ifelse(key=='human', upper, value),
         ci.lower = ifelse(key=='human', lower, value))

@@

@@

@@

s = seq(-1,2.5,0.01)
y = Gdist(0,1,x)

illustration <- data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "low accuracy", type='Disambiguation') %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.5, s), rep = "2", case = "low accuracy", type='Disambiguation')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "high accuracy", type='Disambiguation')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=1.1, Vr=0.5, s), rep = "2", case = "high accuracy", type='Disambiguation')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "low accuracy", type='Development')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.5, s), rep = "2", case = "low accuracy", type='Development')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.1, s), rep = "1", case = "high accuracy", type='Development')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.1, s), rep = "2", case = "high accuracy", type='Development'))

@@

ggplot(illustration, aes(x=x, y=y, linetype=rep)) + 
  geom_line() + 
  theme_few()+
  theme(legend.title = element_text(size=11),
      legend.text=element_text(size=11),
      axis.text = element_text(size = 11),
      strip.text = element_text(size = 11),
      aspect.ratio = 0.5
      )+
  #xlim(c(-1,1))+
  #ylim(c(0,1))+
  #geom_vline(xintercept = 0.0, color="red") +
  #geom_segment(aes(x = 0, y = 0, xend = 0, yend = y, colour = rep),
  #             position=position_dodge(width = .2), 
   #            data = subset(illustration, x==0))+

  geom_col(aes(x = x, y = y, fill = rep),
               position=position_dodge(), 
               width=0.2,
               data = subset(illustration, x==0))+
  geom_text(aes(label=paste("Acc=", prob, sep="")),
            x=2, y=1, size=4, 
            fontface = "bold",
            data=probs)+
  xlab("Perceptual space") + ylab("Prob") +
  facet_grid(type~case) +
  theme(legend.position="none")

@@

>>>>

#The following is a test with adult pilot data
#d_adult <- read_delim("adults_final.txt", delim = " ")  %>%
d_adult <- read_delim("adults_100.txt", delim = " ")  %>%
  filter(type == "Test", #Here I will  filter out particiapants whose first language is arabic or hindi
         other != "yes") %>%
  mutate(iscorrect=ifelse(answer==correct, 1, 0))

@@

d_adult_good <- d_adult %>%
  left_join(d_adult_excl) %>%
  filter(score == 1) %>%
  filter(sound_dist != 'catch')

feather::write_feather(d_adult_good, "../saved_data/data_adult.feather")
```

@@

feather::write_feather(d_child_good, "../saved_data/data_child.feather")

@@

Plot children
```{r}

@@

plot_child <- ggplot(sum_child, 
      aes(x = sound_dist, y = mean, group = factor(concept_dist), col = factor(concept_dist))) +
  #geom_point()+
  geom_pointrange(aes(ymin = lower, ymax = upper), 
                 position = position_dodge(width = .1)) + 
  geom_line() + 
  geom_hline(yintercept = 0.50, linetype="dashed") +
  xlab("Auditory similary") +ylab("Accuracy")+
  scale_colour_discrete(name="Visual similarity")+
  theme_few()+
theme(legend.title = element_text(size=11),
      legend.text=element_text(size=11),
      axis.text = element_text(size = 11)
      )# + facet_grid(.~block)

@@

  #scale_y_continuous(limits = c(0.45, 0.9))+
  theme_few()+
theme(legend.title = element_text(size=11),
      legend.text=element_text(size=11),
      axis.text = element_text(size = 11)
      ) #+ facet_grid(. ~ block)

@@

Regression Model
```{r}

@@

#Add a centerd variable for age group and combine both data 
data_both_ch <- data_ch %>%
  select(ID, c_dist, s_dist, item_object, item_sound, iscorrect) %>%
  mutate(age = -1)

@@

```{r}
#Process the data to prepare for the fit

#Extract distance values
dist_sim_c <- round(d_sim_process$mean[which(d_sim_process$condition=='obj_real' & d_sim_process$labels=='similar')],2)
dist_inter_c <- round(d_sim_process$mean[which(d_sim_process$condition=='obj_real' & d_sim_process$labels=='intermediate')],2)
dist_diff_c <- round(d_sim_process$mean[which(d_sim_process$condition=='obj_real' & d_sim_process$labels=='different')],2)

dist_sim_s <- d_sim_process$mean[which(d_sim_process$condition=='sound_real' & d_sim_process$labels=='similar')]
dist_inter_s <- d_sim_process$mean[which(d_sim_process$condition=='sound_real' & d_sim_process$labels=='intermediate')]
dist_diff_s <- d_sim_process$mean[which(d_sim_process$condition=='sound_real' & d_sim_process$labels=='different')]

#Here normalize the sound with respect to the most distant pair

dist_sim_s <- round(dist_sim_s/dist_diff_s,2)
dist_inter_s <- round(dist_inter_s/dist_diff_s,2)
dist_diff_s <- round(dist_diff_s/dist_diff_s,2)

#For adults: use the similar vs. intermediate pairs
data_fit_adult <- sum_adult %>%
  rename(lower  = lower.ci,
         upper = upper.ci) %>%
  mutate(group = 'adults',
         s_dist = ifelse(sound_dist =='different',  dist_inter_s, dist_sim_s),
         c_dist = ifelse(concept_dist =='different', dist_inter_c, dist_sim_c))

#For children: use the intermediate vs. different pairs 
data_fit_child <- sum_child %>% 
   mutate(group = 'children',
         s_dist = ifelse(sound_dist =='different',  dist_diff_s, dist_inter_s),
         c_dist = ifelse(concept_dist =='different', dist_diff_c, dist_inter_c))

@@

Now I need to predict the mean accuracy as a function of sound and meaning similarity 
```{r}

@@

no_combine_cues <- function(s, o, Vr) {
  s1 = 0
  o1 = 0

   no_acc <- exp(-(s1-s)^2/(2*(Vr)^2)) 
  acc <- 1 
  acc_norm <- acc/(acc+no_acc)

@@

fit_adults_no <- nls(mean ~ no_combine_cues(s_dist, c_dist, Vr), data=subset(data_fit, group=='adults'), start=list(Vr=0.5), lower=c(0), algorithm="port")

@@

Vr_ad <- coef(fit_adults)
Vr_ad_no <- coef(fit_adults_no)
Vr_s_ad <- coef(fit_adults_2)[1]
Vr_o_ad <- coef(fit_adults_2)[2]

@@

fit_children_no <- nls(mean ~ no_combine_cues(s_dist, c_dist, Vr), data=subset(data_fit, group=='children'), start=list(Vr=0.5), lower=c(0), algorithm="port")

@@

Vr_ch <- coef(fit_children)
Vr_ch_no <- coef(fit_children_no)
Vr_s_ch <- coef(fit_children_2)[1]
Vr_o_ch <- coef(fit_children_2)[2]

@@

model_no_val <- as.data.frame(confint2(fit_children_no)) %>%
  mutate(val= Vr_ch_no, 
         model=1, 
         group = "children") %>%
  bind_rows(as.data.frame(confint2(fit_adults)) %>%
              mutate(val= Vr_ad_no, 
                     model=1, 
                     group = "adults"))

@@

#model_comparison <- tibble::rownames_to_column(AIC(fit_adults, fit_adults_2), 'model') %>%
#  bind_rows(tibble::rownames_to_column(AIC(fit_children, fit_children_2), 'model'))

feather::write_feather(model1_val, "../saved_data/values_mod1.feather")  
feather::write_feather(model_no_val, "../saved_data/values_mod_no.feather")

feather::write_feather(model2_val, "../saved_data/values_mod2.feather")

#feather::write_feather(model_comparison, "../saved_data/model_comparison.feather")

@@

model_data <- data_fit %>%
  mutate(prediction = ifelse(group=='adults', 
                             combine_cues(s_dist, c_dist, Vr_ad),
                             combine_cues(s_dist, c_dist, Vr_ch)
                             )) %>%
  mutate(prediction_no = ifelse(group=='adults', 
                             no_combine_cues(s_dist, c_dist, Vr_ad_no),
                             no_combine_cues(s_dist, c_dist, Vr_ch_no)
                             )) %>%
  mutate(prediction_2 = ifelse(group=='adults', 
                             combine_cues_2(s_dist, c_dist, Vr_s_ad, Vr_o_ad),
                             combine_cues_2(s_dist, c_dist, Vr_s_ch, Vr_o_ch)
                             )) %>%
  rename(human = mean)

feather::write_feather(model_data, "../saved_data/data_correlations.feather")
R2_model1 <-  round(cor(model_data$human, model_data$prediction)^2, 2)
R2_model_no <-  round(cor(model_data$human, model_data$prediction_no)^2, 2)
R2_model2 <-  round(cor(model_data$human, model_data$prediction_2)^2, 2)

model_data_plot <-  model_data %>%
  gather(key, value, prediction, prediction_no, prediction_2) #%>%
  #mutate(ci.upper = ifelse(key=='human', upper, value),
  #       ci.lower = ifelse(key=='human', lower, value))

@@

ggplot(subset(model_data_plot, key == "human"), 
      aes(x = sound_dist, y = value, 
          group = factor(concept_dist), 
          col = factor(concept_dist)
          )) +
  #geom_point()+
  geom_pointrange(aes(ymin = ci.lower, ymax = ci.upper), 
                 position = position_dodge(width = .1),
                 size=0.2) + 
  geom_line() + 
  geom_line(data=subset(model_data_plot, key == "prediction"), linetype=2, size=0.5, col='black')+
  geom_point(data=subset(model_data_plot, key == "prediction"), size=1, col='black')+
  geom_hline(yintercept = 0.50, linetype="dashed") +
  xlab("Auditory similary") +ylab("Accuracy")+
  scale_colour_discrete(name="Visual similarity")+
  theme_few()+
theme(legend.title = element_text(size=11),
      legend.text=element_text(size=11),
      axis.text = element_text(size = 11)
      ) + facet_grid(.~group) +
  theme(aspect.ratio = 0.7)

@@

x <- 0

@@

s = seq(-1.5,4,0.01)
y = Gdist(0,1,x)

illustration <- data.frame(x=s, y=Gdist(s0=0, Vr=1, s), rep = "1", case = "low accuracy", type='Disambiguation') %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=2, Vr=1, s), rep = "2", case = "low accuracy", type='Disambiguation')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=1, Vr=0.5, s), rep = "1", case = "high accuracy", type='Disambiguation')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=2, Vr=0.5, s), rep = "2", case = "high accuracy", type='Disambiguation')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=1, Vr=0.5, s), rep = "1", case = "low accuracy", type='Development')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=1, Vr=0.5, s), rep = "2", case = "low accuracy", type='Development')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.1, s), rep = "1", case = "high accuracy", type='Development')) %>%
  bind_rows(data.frame(x=s, y=Gdist(s0=2, Vr=0.1, s), rep = "2", case = "high accuracy", type='Development'))

@@

ggplot(illustration, aes(x=x, y=y, col=rep)) + 
  geom_line() + 
  theme_few()+
  theme(legend.title = element_text(size=11),
      legend.text=element_text(size=11),
      axis.text = element_text(size = 11),
      strip.text = element_text(size = 11),
      aspect.ratio = 0.5
      )+
  #geom_col(aes(x = x, y = y, fill = rep),
  #             position=position_dodge(), 
  #             width=0.2,
  #             data = subset(illustration, x==0))+
  #geom_text(aes(label=paste("Acc=", prob, sep="")),
  #          x=2, y=1, size=4, 
  #          fontface = "bold",
  #          data=probs)+
  xlab("Perceptual space") + ylab("Prob") +
  facet_grid(type~case) +
  theme(legend.position="none")
  #xlim(c(-1,3))

@@

Regression

```{r}
data_ch <- d_child_good %>%
  mutate(s_dist=ifelse(sound_dist=="similar", -1,1),
         c_dist=ifelse(concept_dist=="similar", -1, 1)) %>%
  rename(accuracy = iscorrect)

data_ad <- d_adult_good %>%
  mutate(s_dist=ifelse(sound_dist=="similar", -1,1),
         c_dist=ifelse(concept_dist=="similar", -1, 1)) %>%
  rename(accuracy = iscorrect)

#Combine both  
data_both_ch <- data_ch %>%
  select(ID, c_dist, s_dist, item_object, item_sound, accuracy) %>%
  mutate(age = -1)

data_both_ad <- data_ad %>%
  select(ID, c_dist, s_dist, concept, sound, accuracy) %>%
  rename(item_object = concept,
         item_sound = sound) %>%
  mutate(age = 1) %>%
  mutate(ID2 = sub("+$", "_ad", ID)) %>%
  select(-ID) %>%
  rename(ID=ID2)

model_both <- glmer(accuracy ~ s_dist * c_dist * age+ 
                 (s_dist * c_dist  | ID) + 
                 (c_dist | item_object) + 
                 (s_dist | item_sound) +
                 (s_dist * c_dist | age), 
               data = data_both, family = binomial(),
               glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

model_coef <- tibble::rownames_to_column(as.data.frame(coef(summary(model_both))), "effect")

feather::write_feather(model_coef, "../saved_data/model_regression.feather")
